% Print the title with above letter information
%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------




\begin{cvletter}
\text{\\ \\ \\}
\newline
\newline
\newline
\lettersection{Self Promotion}
I am Yu-Hong Shen, characterized by a conscientious, disciplined, and resolutely studious nature. These personal traits are reflected in my academic pursuits. My cumulative GPA stands at 4.21, equivalent to 97.05 on a percentile scale, positioning me within the 12th (6$\%$) of my department. Beyond my scholastic accomplishments, I possess commendable proficiency in foreign languages, as demonstrated by my achievement of a score of 965 in the TOEIC examination conducted in January 31, 2021.

Besides showcasing unwavering dedication to every task, I embody a proactive ethos. Originally enrolled in the Department of Information Management and Finance, during my freshman year, I discovered a profound interest and innate aptitude for programming. Consequently, I actively seized the opportunity to transfer to the Department of Computer Science. Furthermore, upon acquainting myself with the realm of artificial intelligence during my sophomore year, I became captivated by this field. Hence, in the latter half of my sophomore year, I sought entry into Professor Yiting Chen's laboratory, commencing advanced research one semester ahead of my peers.

Moreover, I am inherently inclined towards exploring new frontiers. Throughout my university journey, I actively engaged with various facets of the computer science domain. I enrolled in diverse courses encompassing computer networks, hardware design, cryptography, computational theories, and system administration. This deliberate exposure significantly enriched and broadened my comprehension within the field. In addition, I utilized my spare time for learning and mastering new skills. During summer breaks, I dedicated myself to developing personal projects. I created two small-scale games and developed two utility tools tailored to address specific needs. Throughout this process, I independently acquired experience in Kotlin, further enhancing my familiarity with Python, which I self-taught during my high school years.

Furthermore, I possess adept communication, coordination, teamwork, and leadership skills. Whether in collaborative end-of-term projects or during the recent October Meizhu Hackathon programming competition, I consistently demonstrate an active approach, willingly undertaking complex and technically challenging segments of projects. In the Meizhu Hackathon programming competition, I played the role of team leader, leading our team into developing an Android accessbility prject. I took charge of orchestrating our work plan, organizing schedules, spreading the workload among team members, and fostering consensus among team members. By excellent communication and effective division of tasks, we ultimately finished our work successfully and attained third place in the competition.


As someone who values innovation and forward-thinking approaches in technology, I am impressed by LINE's dedication to pushing the boundaries of what's possible. While my current focus may lie outside of AI and Android development, I am excited about the opportunity to contribute to LINE's success in other areas. With my professionalism and creative mindset, I am eager to apply for the internship position at LINE, ready to bring fresh perspectives and contribute to the company's ongoing evolution.

Thanks for your time and consideration.


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
